---
title: "AE-CH7"
author: "Your Name Here"
format: 
  html:
    self-contained: true
    toc: true
    toc_float: true
    number_section: false
    highlight: "tango"
    theme: "cosmo"
    df-print: paged
editor: visual
editor_options: 
  chunk_output_type: console
---

This Application Exercise walks through the guided activities in Chapter 7 of the textbook. There are spaces for you to answer each question (with code and/or text). Feel free to also use this document to add your own notes along the way.

## Load packages & data

```{r}
#| label: load-packages-data
#| message: false
#| warning: false

library(tidyverse)
library(janitor) #for clean_names()
library(broom) #for tidy()
library(cowplot) #for plot_grid()
shuttle <- read_csv("./data/C7 Shuttle.csv") %>% 
  clean_names()
```

## Question 1

Explanatory:

Response:

## Question 2

Imagine you're an engineer working for Thiokol Corporation prior to January 1986. Create a few graphs of the `shuttle` data.

```{r}

```

## Question 3

```{r}

```

What's the problem with these predictions?

\[Q4 - done in class together, skip Q5\]

## Question 6

Calculate the MLE estimates of $\beta_0$ and $\beta_1$. Compare the MLE estimates to the OLS estimates in Q3.

```{r}

```

## Question 7

Use the MLE estimates and the following equation to predict the probability that a launch has no O-ring damage when the temperature is 31, 50, and 75 degrees Fahrenheit.

$$\hat{\pi}_i = \frac{e^{b_0+b_1x_i}}{1 + e^{b_0+b_1x_i}}$$

```{r}

```

## Question 8

```{r}

```

## Question 9

```{r}

```

## Question 10

## Question 11

```{r}

```

## Question 12

```{r}

```

## Question 13

```{r}

```

## 
