---
title: "AE-CH4"
author: "Your Name Here"
format: 
  html:
    self-contained: true
    toc: true
    toc_float: true
    number_section: false
    highlight: "tango"
    theme: "cosmo"
    df-print: paged
editor: visual
editor_options: 
  chunk_output_type: console
---

This Application Exercise walks through the guided activities in Chapter 4 of the textbook. There are spaces for you to answer each question (with code and/or text). Feel free to also use this document to add your own notes along the way.

```{r}
#| label: load-packages
#| message: false
#| warning: false

library(tidyverse)
library(janitor)
library(broom)
library(cowplot)
```

```{r}
#| label: load-data
#| message: false
#| warning: false

popcorn <- read_csv("./data/C4 Popcorn.csv") %>% 
  clean_names()
```

## Question 1

*Don't need to list them out*

> YOUR ANSWER HERE

## Question 2

> YOUR ANSWER HERE

## Question 3

> YOUR ANSWER HERE

## Question 4

```{r}

```

## Question 5

```{r}

```

## Question 6

*Hint: see Table 4.3*

> YOUR ANSWER HERE

## Questions 8 - 10

\[Already completed for you\]. The following code calculates the three measures of between-group variability (MSBrand, MSTime, MSBrandTime), and the within-group variability MSE. See Equations 4.1 - 4.4.

```{r}
popcorn %>% 
  mutate(ybar_grand = mean(pop_rate)) -> popcorn

#MSBrand - see equation 4.1
popcorn %>% 
  group_by(brand, ybar_grand) %>% 
  summarize(n_brand = n(),
         ybar_brand = mean(pop_rate)) %>% 
  mutate(term  = n_brand*(ybar_brand - ybar_grand)^2) %>% 
  ungroup() %>% 
  summarize(MSBrand = sum(term)/(2-1)) %>% 
  pull(MSBrand) -> MSBrand
MSBrand

#MSTime - see equation 4.2
popcorn %>% 
  group_by(time, ybar_grand) %>% 
  summarize(n_time = n(),
         ybar_time = mean(pop_rate)) %>% 
  mutate(term  = n_time*(ybar_time - ybar_grand)^2) %>% 
  ungroup() %>% 
  summarize(MSTime = sum(term)/(2-1)) %>% 
  pull(MSTime) -> MSTime
MSTime

#MSBrandTime - see equation 4.3
popcorn %>% 
  group_by(time, brand, ybar_grand) %>% 
  summarize(n_timebrand = n(),
         ybar_timebrand = mean(pop_rate)) %>% 
  mutate(term  = n_timebrand*(ybar_timebrand - ybar_grand)^2) %>% 
  ungroup() %>% 
  summarize(MSTimeBrand = (sum(term) - MSTime*(2-1) - MSBrand*(2-1))/(4 - 1-1-1)) -> MSTimeBrand
MSTimeBrand

#MSE - see equation 4.4
popcorn %>% 
  group_by(time, brand) %>% 
  summarize(n_ij = n(),
            s2_ij = var(pop_rate)) %>% 
  mutate(term  = (n_ij - 1)*s2_ij) %>% 
  ungroup() %>% 
  summarize(MSE = sum(term)/sum(n_ij - 1))
```

## Question 11

```{r}

```

## Question 12

> YOUR ANSWER HERE

## Interaction plot (Fig 4.2)

```{r}
#interaction plot
popcorn %>% 
  group_by(time, brand) %>% 
  summarize(mean = mean(pop_rate)) %>% 
  ggplot(aes(y = mean, x = time, 
             group = brand, color = brand)) +
  geom_point() +
  geom_line() +
  labs(x = "Cook time",
       y = "Average pop rate",
       title = "Interaction Plot") +
  scale_color_viridis_d() +
  theme_minimal()
```

## Main Effects plot

```{r}
#main effects plot


#main effects plot for microwave factor
popcorn %>% 
  group_by(microwave) %>% 
  summarize(mean = mean(pop_rate)) %>% 
  ggplot(aes(y = mean, x = microwave,
             group = 1)) +
  geom_point() +
  geom_line() +
  ylim(78, 85) +
  labs(x = "level",
       y = "Average pop rate")

#create a generic function to create a main effects plot
#for any data & explanatory/response variable
main_effects_plot <- function(data, 
                              explanatory_variable, 
                              response_variable,
                              ylimits,
                              labels){
  data %>% 
    #!!sym() is just the syntax used to pass a string 
    #to a variable name to be used in a tidyverse fxn
    group_by(!!sym(explanatory_variable)) %>% 
    summarize(mean = mean(!!sym(response_variable))) %>% 
    ggplot(aes(y = mean, x = !!sym(explanatory_variable),
             group = 1)) +
    geom_point() +
    geom_line() +
    ylim(ylimits[1], ylimits[2]) +
    labs(x = labels[1],
         y = labels[2])
}
#create main effects plot for microwave factor
#(and save as object p1)
p1 <- main_effects_plot(popcorn, "microwave", "pop_rate",
                  c(75, 85),
                  c("level", "Average pop rate"))

#create main effects plot for brand factor
#(and save as object p2)
p2 <- main_effects_plot(popcorn, "brand", "pop_rate",
                  c(75, 85),
                  c("level", "Average pop rate"))
#create main effects plot for time factor
#(and save as object p3)
p3 <- main_effects_plot(popcorn, "time", "pop_rate",
                  c(75, 85),
                  c("level", "Average pop rate"))
#use plot_grid() from cowplot package to arrange several plots
plot_grid(p1, p2, p3, nrow = 1)
```

## Question 13

Fit an appropriate anova model and view the results.

```{r}

```

## Question 14

> YOUR ANSWER HERE

## Question 15

```{r}

```

## Question 16

```{r}

```

> YOUR ANSWER HERE

## Question 17

```{r}

```

> YOUR ANSWER HERE

## Question 18

```{r}

```

> YOUR ANSWER HERE

## Question 19

> YOUR ANSWER HERE
