---
title: "AE-CH2"
author: "Your Name Here"
format: 
  html:
    self-contained: true
    toc: true
    toc_float: true
    number_section: false
    highlight: "tango"
    theme: "cosmo"
    df-print: paged
editor: visual
editor_options: 
  chunk_output_type: console
---

This Application Exercise walks through the guided activities in Chapter 2 of the textbook. There are spaces for you to answer each question (with code and/or text). Feel free to also use this document to add your own notes along the way. 

```{r}
#| label: load-packages
#| message: false
#| warning: false

library(tidyverse)
library(janitor)
library(ggridges)
library(infer)
library(broom)
```

```{r}
#| label: load-data
#| message: false
#| warning: false

games1 <- read_csv("./data/C2 Games1.csv") %>% 
  clean_names()
```

### Question 1

> YOUR ANSWER HERE

### Question 2

> YOUR ANSWER HERE

### Question 3

> YOUR ANSWER HERE

### Question 4

```{r boxplot}
ggplot(games1, aes(y = time, x = type)) +
  geom_boxplot()
```

> YOUR ANSWER HERE

```{r summary-stats}
games1 %>% 
  group_by(type) %>% 
  summarize(ybar = mean(time),
            s = sd(time))
```

[Skip Q5 & Q6]

### Question 7

```{r}
#compute residuals
games1 <- games1 %>% 
  group_by(type) %>% 
  mutate(ybar = mean(time),
         residual = time - ybar)

#histogram of residuals

  
```

> YOUR ANSWER HERE

### Question 8

```{r}
#informal test of equal variance

#create data for group 1
data1 <- games1 %>% filter(type == "Color")
#compute s1
s1 <- sd(data1$time)

#create data for group 2

#compute s2

#informal test

```

> YOUR ANSWER HERE

### Question 9

```{r}

```

> YOUR ANSWER HERE

### Question 10

```{r}
t_test(games1, response = time, 
       explanatory = type)
```

> YOUR ANSWER HERE

### Question 11

```{r}
games1 <- games1 %>% 
  mutate(type_recoded = factor(type, 
                       levels = c("Standard",
                                  "Color")))
m1 <- lm(time ~ type_recoded, data = games1)
tidy(m1)
```

### Question 12

```{r}
confint(m1)
```

> YOUR ANSWER HERE

### Question 13

```{r}

m2 <- lm(time ~ type, data = games1)
tidy(m2)
confint(m2)
```

> YOUR ANSWER HERE

### Question 14

```{r}
#create augmented dataset with residuals
m1_aug <- augment(m1)
#add student id variable back in
m1_aug$student_id <- games1$student_id

ggplot(m1_aug, aes(x = .resid)) +
  geom_histogram(binwidth = 2, color = "white")

ggplot(m1_aug, aes(x = student_id, y = .resid)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```

> YOUR ANSWER HERE

### Question 15

```{r}
games1 <- games1 %>% 
  mutate(type_01 = if_else(type == "Color", 1, 0))

ggplot(games1, aes(y = time, x = type_01)) +
  geom_smooth(method = "lm", se = FALSE) +
  geom_point()
tidy(m1)
```

> YOUR ANSWER HERE

### Question 16

> YOUR ANSWER HERE

### Question 17

> YOUR ANSWER HERE

### Question 18

> YOUR ANSWER HERE

### Question 19

```{r}
#compute grand mean
grand_mean <- mean(games1$time)

#compute mean for group 1 (color)
ybar1dot <- mean(data1$time)

#compute mean for group 2 (standard)
```

### Question 20

```{r}
#effect size color 


#effect size standard

```

### COMPARE RESIDUALS

```{r}
#compute residuals for regression model
#store as new variable res_reg in games1 dataset
# do same for ANOVA residuals, call res_aov



```


### Question 23

```{r}
aov_m1 <- anova(m1)
tidy(aov_m1)
```

> YOUR ANSWER HERE

### Question 24

> YOUR ANSWER HERE

### Question 25

> YOUR ANSWER HERE

### Question 26

```{r}

```

> YOUR ANSWER HERE

### Question 27

> YOUR ANSWER HERE
