---
title: "AE-CH5"
author: "Your Name Here"
format: 
  html:
    self-contained: true
    toc: true
    toc_float: true
    number_section: false
    highlight: "tango"
    theme: "cosmo"
    df-print: paged
editor: visual
editor_options: 
  chunk_output_type: console
---

This Application Exercise walks through the guided activities in Chapter 5 of the textbook. There are spaces for you to answer each question (with code and/or text). Feel free to also use this document to add your own notes along the way.

```{r}
#| label: load-packages
#| message: false
#| warning: false

library(tidyverse)
library(janitor)
library(broom)
library(cowplot)
library(lme4)
```

```{r}
#| label: load-data
#| message: false
#| warning: false

memory <- read_csv("./data/C5 Memory.csv") %>% 
  clean_names()
```

## Question 1

### Part a

$$
H_0: \alpha_1 = \alpha_2
$$

$$
H_A: \alpha_1 \neq \alpha_2
$$

$$
H_0: \beta_1 = \beta_2
$$

$$
H_A: \beta_1 \neq \beta_2
$$

$$
H_0: (\alpha\beta)_{11} = (\alpha\beta)_{12} = (\alpha\beta)_{21} = (\alpha\beta)_{22}
$$

$$
H_A: \text{at least one } (\alpha\beta)_{ij} \text{ differs}
$$

### Part b

```{r}
m1 <- aov(lm(score ~ wordlist*distracter,
               data = memory))
tidy(m1)
```

### Part c

```{r}
#individual value plot
ggplot(memory, aes(x = wordlist, 
                   y = score)) +
  facet_wrap(~distracter) +
  geom_point()

#residuals
memory <- memory %>% 
  mutate(residuals = m1$residuals)

ggplot(memory, aes(x = residuals)) +
  geom_histogram(color = "white",
                 bins = 10)
```

### Part d

```{r}
main_effects_plot <- function(data, 
                              explanatory_variable, 
                              response_variable){
  data %>% 
    #!!sym() is just the syntax used to pass a string 
    #to a variable name to be used in a tidyverse fxn
    group_by(!!sym(explanatory_variable)) %>% 
    summarize(mean = mean(!!sym(response_variable))) %>% 
    ggplot(aes(y = mean, x = !!sym(explanatory_variable),
             group = 1)) +
    geom_point() +
    geom_line() +
    theme_minimal()
}

p1 <- main_effects_plot(memory, "wordlist", "score") + ylim(7, 9)
p2 <- main_effects_plot(memory, "distracter", "score") + ylim(7, 9)
plot_grid(p1, p2)

#interaction plot
memory %>% 
  group_by(wordlist, distracter) %>% 
  summarize(mean = mean(score)) %>% 
  ggplot(aes(y = mean, x = wordlist, 
             group = distracter, 
             color = distracter)) +
  geom_point() +
  geom_line() +
  labs(x = "Word list type",
       y = "Memory score",
       title = "Interaction Plot") +
  scale_color_viridis_d() +
  theme_minimal()
```

> YOUR ANSWER HERE

## Question 2

### Part a

```{r}
memory <- memory %>% 
  mutate(student = factor(student))
m2 <- aov(lm(score ~ wordlist*distracter + student,
               data = memory))
tidy(m2)
```

> YOUR ANSWER HERE

### Part b

> YOUR ANSWER HERE

### Part c

```{r}
p1 <- main_effects_plot(memory, "wordlist", "score") + ylim(5,12)
p2 <- main_effects_plot(memory, "distracter", "score") + ylim(5,12)
p3 <- main_effects_plot(memory, "student", "score") + ylim(5,12)
plot_grid(p1, p2, p3)

```

### Part d

```{r}
memory <- memory %>% 
  mutate(residuals_m2 = m2$residuals)

ggplot(memory, aes(x = residuals_m2)) +
  geom_histogram(color = "white",
                 bins = 10)
```

## Question 3

> YOUR ANSWER HERE

## Question 4

> YOUR ANSWER HERE

## Question 5

> YOUR ANSWER HERE

## Question 6

> YOUR ANSWER HERE

## Question 7

```{r}
memory <- memory %>% 
  mutate(student2 = factor(student2))
m3 <- lmer(score ~ wordlist*distracter + (1|major/student2),
           data = memory)
anova(m3)
m4 <- aov(lm(score ~ wordlist*distracter + major + student2,
           data = memory))
tidy(m4)

m5 <- aov(score ~ wordlist*distracter + Error(major/student2),
           data = memory)
tidy(m5)
```
