---
title: "AE-CH7"
author: "Your Name Here"
format: 
  html:
    self-contained: true
    toc: true
    toc_float: true
    number_section: false
    highlight: "tango"
    theme: "cosmo"
    df-print: paged
editor: visual
editor_options: 
  chunk_output_type: console
---

This Application Exercise walks through the guided activities in Chapter 7 of the textbook. There are spaces for you to answer each question (with code and/or text). Feel free to also use this document to add your own notes along the way.

## Load packages & data

```{r}
#| label: load-packages-data
#| message: false
#| warning: false

```


## Question 1

## Question 2

```{r}

```

## Question 3

```{r}

```

What's the problem with these predictions? 

[Skip Q4 - done in class together]

## Question 5

```{r}

```


## Question 6

```{r}

```

## Question 7

$$\hat{\pi}_i = \frac{e^{b_0+b_1x_i}}{1 + e^{b_0+b_1x_i}}$$

```{r}

```

## Question 8

```{r}

```


## Question 9

```{r}

```

## Question 10


## Question 11

```{r}

```

## Question 12

```{r}

```


## Question 13

```{r}

```


## Question 14

```{r}

```

## Question 15

```{r}

```


## Question 16

```{r}

```


## Question 17

```{r}

```


## Question 18

```{r}

```

