---
title: "AE-CH9"
author: "Your Name Here"
format: 
  html:
    self-contained: true
    toc: true
    toc_float: true
    number_section: false
    highlight: "tango"
    theme: "cosmo"
    df-print: paged
editor: visual
editor_options: 
  chunk_output_type: console
---

This Application Exercise walks through the guided activities in Chapter 9 of the textbook. There are spaces for you to answer each question (with code and/or text). Feel free to also use this document to add your own notes along the way.

## Load packages & data

```{r}
#| label: load-packages-data
#| message: false
#| warning: false

library(tidyverse)
library(janitor)
library()
melt <- read_csv("./data/C9 MeltingChipsJS.csv") %>% 
  clean_names()
```

## Question 2

> **event of interest**: 

> **time-to-event random variable**: 

> **beginning of time**: 

> **scale for measuring time**:

## Question 3

How many melting times are complete? How many are censored? 

```{r}
#first fix poorly named column! 
melt <- melt %>% 
  mutate(complete = censor,
         censored = if_else(complete == 0, 1, 0)) %>% 
  select(-censor)

#count of complete vs. incomplete

```

## Question 4

$\hat{S}(25)_E$

$\hat{S}(30)_E$

$\hat{S}(40)_E$

$\hat{S}(60)_E$

## Question 5

### Part a

$\hat{S}(45)_E = $

### Part b

$\hat{S}(45)_E = $


## Questions 6 - 13

$m =$

| Interval $i$ | $t_i$ | Time interval | $n_i$ | Number censored | $d_i$ | $\hat{p}_i$ | $1 - \hat{p}_i$ | $\hat{S}(t)_{KM}$ |
|-----|-----|-----|-----|-----|-----|-----|-----|-----|
|0 | 0 | [0, 25) | | | | | | | 
|1 | 25| [25, 30) | | | | | | |

....


## Question 14



## Question 15

```{r}

```

## Question 16

```{r}

```

[Skip 17]

## Question 18


## Question 19

```{r}

```

[Skip 20 - 24]

## Question 25

```{r}

```

[Skip 27 - 28]

## Question 29

```{r}

```

## Question 30

## Question 31

## Question 36

