---
title: "HW Bayes 01"
author: "Your Name Here"
format: 
  html:
    self-contained: true
    toc: true
    toc_float: true
    number_section: false
    highlight: "tango"
    theme: "cosmo"
    df-print: paged
editor: visual
editor_options: 
  chunk_output_type: console
---

## Instructions

This Homework comes from Chapters 1 & 2 of the [Bayes Rules! Textbook](https://www.bayesrulesbook.com/). The questions chosen for this week's homework should be answerable based on prior statistical knowledge and the Bayesian activities done in class during Week 11. However, in Week 12 you will be asked to read the full Chapters 1 & 2 of this textbook, so you may find the reading useful for this homework, too.

### [Chapter 1 Exercises](https://www.bayesrulesbook.com/chapter-1#exercises):

-   1.1

-   Choose 1.3 or 1.4

### [Chapter 2 Exercises:](https://www.bayesrulesbook.com/chapter-2#exercises-1)

-   2.1

-   2.2

-   2.4

-   2.9

```{r}
#| label: load-packages
#| message: false
#| warning: false

```

## 1.1

#### Part a

> YOUR ANSWER HERE

#### Part b

> YOUR ANSWER HERE

#### Part c

> YOUR ANSWER HERE

## 1.3 OR 1.4

\[INSERT IMAGE HERE\]

## 2.1

#### Part a

> YOUR ANSWER HERE

#### Part b

> YOUR ANSWER HERE

#### Part c

> YOUR ANSWER HERE

#### Part d

> YOUR ANSWER HERE

## 2.2

#### Part a

> YOUR ANSWER HERE

#### Part b

> YOUR ANSWER HERE

#### Part c

> YOUR ANSWER HERE

#### Part d

> YOUR ANSWER HERE

#### Part e

> YOUR ANSWER HERE

#### Part f

> YOUR ANSWER HERE

## 2.4

```{r}
#show your calculations
```

> YOUR ANSWER HERE

## 2.9

#### Part a

*\[Create a table in this Quarto document. Hint: See "Table" dropdown in the Visual tab.\]*

#### Part b

*\[Note "normalizing constant" is another term for the "marginal probability" that goes on the denominator in Bayes Rule\]*

```{r}
#show your calculations
```

> YOUR ANSWER HERE

#### Part c

```{r}
#show your calculations
```

> YOUR ANSWER HERE

#### Part d

```{r}
#show your calculations
```

> YOUR ANSWER HERE

## Reflection prompts

*Respond to each of the following after you have completed all exercises in this assignment*

*(RP1): What were the main concepts covered in this assignment?*

> YOUR ANSWER HERE

*(RP2): What's one thing you understand better after completing these exercises?*

> YOUR ANSWER HERE

*(RP3): What exercise(s) gave you the most trouble? What was difficult about them/where did you get stuck?*

> YOUR ANSWER HERE
