---
title: "HW Bayes 02"
author: "Your Name Here"
format: 
  html:
    self-contained: true
    toc: true
    toc_float: true
    number_section: false
    highlight: "tango"
    theme: "cosmo"
    df-print: paged
editor: visual
editor_options: 
  chunk_output_type: console
---

## Instructions

This Homework comes from Chapters 1 & 2 of the [Bayes Rules! Textbook](https://www.bayesrulesbook.com/). You should complete this assignment after having read the full Chapters 1 & 2 in Week 12.

### [Chapter 1 Exercises](https://www.bayesrulesbook.com/chapter-1#exercises):

-   1.6

-   1.8

### [Chapter 2 Exercises:](https://www.bayesrulesbook.com/chapter-2#exercises-1)

-   2.3

-   2.6

-   2.11

-   2.13

-   2.14

-   2.18

-   2.20

-   2.21

```{r}
#| label: load-packages
#| message: false
#| warning: false

```

## 1.6

#### Part a

> YOUR ANSWER HERE

#### Part b

> YOUR ANSWER HERE

#### Part c

> YOUR ANSWER HERE

## 1.8

#### Part a

> YOUR ANSWER HERE

#### Part b

> YOUR ANSWER HERE

## 2.3

#### Part a

> YOUR ANSWER HERE

#### Part b

> YOUR ANSWER HERE

#### Part c

> YOUR ANSWER HERE

#### Part d

> YOUR ANSWER HERE

#### Part e

> YOUR ANSWER HERE

#### Part f

> YOUR ANSWER HERE

## 2.6

> YOUR ANSWER HERE

## 2.11

#### Part a

> YOUR ANSWER HERE

#### Part b

```{r}

```

> YOUR ANSWER HERE

#### Part c

```{r}

```

> YOUR ANSWER HERE

## 2.13

#### Part a

> YOUR ANSWER HERE

#### Part b

```{r}
#show your calculations
```

> YOUR ANSWER HERE

#### Part c

```{r}
#show your calculations
```

> YOUR ANSWER HERE

## 2.14

#### Part a

> YOUR ANSWER HERE

#### Part b

```{r}
#show your calculations
```

> YOUR ANSWER HERE

#### Part c

> YOUR ANSWER HERE

## 2.18

```{r}

```

## 2.20

```{r}

```

## 2.21

```{r}

```

## Reflection prompts

*Respond to each of the following after you have completed all exercises in this assignment*

*(RP1): What were the main concepts covered in this assignment?*

> YOUR ANSWER HERE

*(RP2): What's one thing you understand better after completing these exercises?*

> YOUR ANSWER HERE

*(RP3): What exercise(s) gave you the most trouble? What was difficult about them/where did you get stuck?*

> YOUR ANSWER HERE
