---
title: "AE-CH8 / HW-CH8"
author: "Your Name Here"
format: 
  html:
    self-contained: true
    toc: true
    toc_float: true
    number_section: false
    highlight: "tango"
    theme: "cosmo"
    df-print: paged
editor: visual
editor_options: 
  chunk_output_type: console
---

This Application Exercise walks through the guided activities in Chapter 8 of the textbook. There are spaces for you to answer each question (with code and/or text). Feel free to also use this document to add your own notes along the way.

## Load packages & data

```{r}
#| label: load-packages-data
#| message: false
#| warning: false
library(tidyverse)
```

# Cancer data

## Question 1

```{r}

```

## Question 2

```{r}

```

## Question 3

```{r}

```

## Question 4

```{r}

```

> YOUR ANSWER HERE

## Question 5

```{r}

```

> YOUR ANSWER HERE

## Question 6

> YOUR ANSWER HERE

## Question 7

> YOUR ANSWER HERE

## Question 8

> YOUR ANSWER HERE

## Question 9

```{r}
years <- 25
n <- 1138
person_years <- n*years
incidence_rate <- 326/100000

#simulate cases for a single neighborhood
rbinom(1, size = person_years, prob = incidence_rate)

#simulate 10,000 neighborhoods

#view summary of simulations
#sanity check- should get mean & median around 93

#plot simulations

#compute p-value
```

## Question 10

```{r}

```

## Skip 11 - 14

## Question 15

```{r}

```

## Question 16

```{r}

```

## Question 17

```{r}

```

> YOUR ANSWER HERE

## Question 18

```{r}

```

> YOUR ANSWER HERE

## Question 19

```{r}

```

## Question 20

```{r}

```

> YOUR ANSWER HERE

## Question 21

```{r}

```

> YOUR ANSWER HERE

## Question 22

```{r}

```

> YOUR ANSWER HERE

## Question 23

```{r}

```

> YOUR ANSWER HERE

## Question 24

> YOUR ANSWER HERE

## Question 25

```{r}

```

> YOUR ANSWER HERE

## Question 26

> YOUR ANSWER HERE

## Question 27

```{r}

```

> YOUR ANSWER HERE

## Question 28

## Question 29

```{r}

```

> YOUR ANSWER HERE

## Question 30

```{r}

```

> YOUR ANSWER HERE

## Question 31

```{r}

```

> YOUR ANSWER HERE

## Question 32

> YOUR ANSWER HERE

## Question 33

```{r}

```

> YOUR ANSWER HERE

## Question 34

```{r}

```

> YOUR ANSWER HERE

# Galapagos

## Question 50

```{r}

```

> YOUR ANSWER HERE

## Question 51

```{r}

```

## Question 52

```{r}

```

> YOUR ANSWER HERE

## Question 53

```{r}

```

> YOUR ANSWER HERE

## Question 54

> YOUR ANSWER HERE

## Question 55

```{r}

```

> YOUR ANSWER HERE

## Question 56

> YOUR ANSWER HERE

## Question 57

```{r}

```

> YOUR ANSWER HERE

## Question 58

*Hint: use family = "quasipoisson" to fit an over-dispersed Poisson model.*

*Sanity check: R will output the deviance values for the regular (non-over-dispersed) model, so they should match those from Q53, but the coefficients should change*

```{r}

```

> YOUR ANSWER HERE

## Question 59


```{r}

```

> YOUR ANSWER HERE
