---
title: "Homework Chapter 2"
author: "Your Name Here"
format: 
  html:
    self-contained: true
    toc: true
    toc_float: true
    number_section: false
    highlight: "tango"
    theme: "cosmo"
    df-print: paged
editor: visual
editor_options: 
  chunk_output_type: console
---

## Instructions

This Homework comes from Chapter 2 of the Textbook. You should refer to AE_CH2 for some template code.

Complete the following exercises:

+ E.2
+ E.4
+ E.6
+ E.7
+ E.8
+ E.13 (skip part d)

```{r}
#| label: load-packages
#| message: false
#| warning: false

library(tidyverse)
library(janitor)
library(ggridges)
library(infer)
library(broom)
```


## E.2

> YOUR ANSWER HERE

## E.4

> YOUR ANSWER HERE

## E.6

```{r}
#| label: load-data2
#| message: false
#| warning: false

games2 <- read_csv("./data/C2 Games2.csv") %>% 
  clean_names()
```

### Part a

```{r}
#plot the data

```

> YOUR ANSWER HERE

### Part b

```{r}
#conduct ANOVA

```

> YOUR ANSWER HERE

### Part c

```{r}
#residual plot

```

> YOUR ANSWER HERE

### Part d

> YOUR ANSWER HERE

### Part e

> YOUR ANSWER HERE

## E.7

### Part a

> YOUR ANSWER HERE

### Part b

```{r}
#graph data
```

> YOUR ANSWER HERE

### Part c

```{r}
#conduct ANOVA
```

> YOUR ANSWER HERE

### Part d

```{r}
#show equal variance violated

#create variable for log(Strength). Note, by default in R, log() computes the natural log

#conduct ANOVA with log(Strength) as outcome


```

> YOUR ANSWER HERE

### Part e

```{r}

```

> YOUR ANSWER HERE

### Part f

> YOUR ANSWER HERE

### Part g

> YOUR ANSWER HERE

## E.8

### Part a

```{r}

```

> YOUR ANSWER HERE

### Part b

```{r}

```

> YOUR ANSWER HERE

### Part c

> YOUR ANSWER HERE

### Part d

> YOUR ANSWER HERE

## E.13

[Read Section 2.9 before completing this exercise]

```{r}
#| label: load-data3
#| message: false
#| warning: false

weights <- read_csv("./data/C2 Weights.csv") %>% 
  clean_names()
```

### Part a

```{r}

```


### Part b

```{r}

```

### Part c

```{r}

```

[skip part d]
