---
title: "HW-CH9"
author: "Your Name Here"
format: 
  html:
    self-contained: true
    toc: true
    toc_float: true
    number_section: false
    highlight: "tango"
    theme: "cosmo"
    df-print: paged
editor: visual
editor_options: 
  chunk_output_type: console
---

## Instructions

This Homework comes from Chapter 9 of the Textbook. You should refer to AE_CH9 for some template code.

Complete the following exercises:

-   E.1 (can access pdfs through APU library website. You may also choose to find a more recent article that uses survival analysis)

-   E.2

-   E.3

-   E.12 (only do `survdiff()` once - don't need log rank and Wilcoxen separately)

-   E.13

-   E.15 (a - c only)

```{r}
#| label: load-packages
#| message: false
#| warning: false

```

## E.1

#### Part a

> YOUR ANSWER HERE

#### Part b

> YOUR ANSWER HERE

#### Part c

> YOUR ANSWER HERE

#### Part d

> YOUR ANSWER HERE


## E.2

#### Part a

> YOUR ANSWER HERE

#### Part b

> YOUR ANSWER HERE

#### Part c

> YOUR ANSWER HERE

## E.3

#### Part a

> YOUR ANSWER HERE

#### Part b

> YOUR ANSWER HERE

#### Part c

> YOUR ANSWER HERE

## E.12

#### Part a

```{r}

```

> YOUR ANSWER HERE

#### Part b

```{r}

```

> YOUR ANSWER HERE

#### Part c

```{r}

```

> YOUR ANSWER HERE

## E.13

#### Part a

```{r}

```

> YOUR ANSWER HERE

#### Part b

```{r}

```


## E.15

#### Part a

```{r}

```

> YOUR ANSWER HERE

#### Part b

```{r}

```

> YOUR ANSWER HERE

#### Part c

```{r}

```

> YOUR ANSWER HERE



## Reflection prompts

*Respond to each of the following after you have completed all exercises in this assignment*

*(RP1): What were the main concepts covered in this assignment?*

> YOUR ANSWER HERE

*(RP2): What's one thing you understand better after completing these exercises?*

> YOUR ANSWER HERE

*(RP3): What exercise(s) gave you the most trouble? What was difficult about them/where did you get stuck?*

> YOUR ANSWER HERE
