---
title: "Homework Chapter 1"
author: "Your Name Here"
format: 
  html:
    self-contained: true
    toc: true
    toc_float: true
    number_section: false
    highlight: "tango"
    theme: "cosmo"
    df-print: paged
editor: visual
editor_options: 
  chunk_output_type: console
---

## Instructions

This Homework comes from Chapter 1 of the Textbook. You should refer to AE_CH1 for some template code.

Complete the following exercises:

-   E.1
-   E.2
-   E.3
-   E.4
-   E.10
-   E.11
-   E.13
-   E.14

```{r}
#| label: load-packages
#| message: false
#| warning: false

library(tidyverse)
library(janitor)
library(infer)
library(broom)
```

## E.1

> YOUR ANSWER HERE

## E.2

> YOUR ANSWER HERE

## E.3

> YOUR ANSWER HERE

## E.4

> YOUR ANSWER HERE

## E.10

> YOUR ANSWER HERE

## E.11

```{r}
#| label: load-data
#| message: false
#| warning: false

mice <- read_csv("./data/C1 Mice.csv") %>% 
  clean_names()
```

### Part a

*Modify the code from the Q7 - Q9 section of AE-CH1*

```{r}


```

> YOUR ANSWER HERE

### Part b

```{r}


```

> YOUR ANSWER HERE

## E.13

### Part a

```{r}

```

> YOUR ANSWER HERE

### Part b

```{r}

```

> YOUR ANSWER HERE

## E.14

### Part a

```{r}

```

> YOUR ANSWER HERE

### Part b

```{r}

```

> YOUR ANSWER HERE

### Part c

```{r}

```

> YOUR ANSWER HERE

## Reflection prompts

*Respond to each of the following after you have completed all exercises in this assignment*

*(RP1): What were the main concepts covered in this assignment?*

> YOUR ANSWER HERE

*(RP2): What's one thing you understand better after completing these exercises?*

> YOUR ANSWER HERE

*(RP3): What exercise(s) gave you the most trouble? What was difficult about them/where did you get stuck?*

> YOUR ANSWER HERE
